\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-11 Articles/IROS/root.tex
added 3d keyframes plot for column

\begin{figure}[h]
	\centering
	\includegraphics[width=0.95\linewidth]{demo-field1.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:example-field}
\end{figure}

@@

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=0.95\linewidth]{demo-field1c.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:example-field}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{keyframes_3D.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:keyframes-3d-column}
\end{figure}
